\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage[english]{babel}
\usepackage{enumitem}%can be used for automatic numbering of requirements/tests.
\usepackage{hyperref}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{color} % Used to write in red,blue,green etc.
\usepackage{float}
\usepackage[titletoc]{appendix}

\newlength{\testlabellength}
\settowidth{\testlabellength}{Instruction 100.10.10}
\newenvironment{testlist}{\begin{enumerate}[label=\bfseries Instruction \thesubsection.\arabic* , labelindent=0pt, labelwidth=\testlabellength , leftmargin=2cm]}{\end{enumerate}}

\newenvironment{precondition}{
{\color{white}BLARG}\\ 
\textbf{Precondition}
\begin{itemize}[labelindent=0cm, labelwidth=2cm , leftmargin=1cm]
}
{\end{itemize}}

\newenvironment{instruction}{
\textbf{Instructions:}
\begin{enumerate}[label=\bfseries  \arabic*., labelindent=0cm, labelwidth=2cm , leftmargin=1cm]
}
{\end{enumerate}}

\newenvironment{postcondition}{
\textbf{Postcondition:}
\begin{itemize}[labelindent=0cm, labelwidth=2cm , leftmargin=1cm]
}
{\end{itemize}}

\title{SVVI - Software Verification and Validation Instruction}
\newcommand{\version}{v0.0}
\newcommand{\SVVI}{PUSS154215}
\author{Testgroup, Team 2}


%-------------------------TITLE-----------------------------------------

\begin{document}
\begin{titlepage}
\newgeometry{left=2cm,top=1cm,right=2cm}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

\begin{minipage}{0.5\textwidth}
\begin{flushleft} % Responsible persons, write on separate lines
\textit{Responsible for this document:}\\
Oskar Fällström %Not entirely sure who this should be, possibly project leaders as well?
\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.4\textwidth}
\begin{flushright}
\SVVI\ \version\ %Dokumentnummer enl. projekthandledning s. 22-23 och insidan av pärmen
\today
\end{flushright}
\end{minipage}\\[3cm]

\centering
\textsc{\LARGE Team 2}\\[0.5cm]

\HRule \\[0.4cm]
{ \huge \bfseries SVVI - Software Verification and Validation Instruction }\\[0.4cm] % Title of your document
\HRule \\[1.5cm]

\vfill
\begin{flushleft}
\textit{Authors of this document:}\\
Måns Andersson \\
Hanna Autio \\
Moa Eklöf \\
Oskar Fällström \\
Ulf Hörndahl \\
Jonathan Lundholm
\end{flushleft}


\end{titlepage}
\pagenumbering{gobble}

\begin{center}
\textit{\large Version History}

    \begin{tabular}{ | l | l | l | p{5cm} |}
    \hline
    \textbf{Version}	& \textbf{Date}	& \textbf{Responsible}		& \textbf{Description}					\\ \hline
    0.0						& 150916 			& UH									& Document created						\\ \hline
    \end{tabular}
\end{center}

\setcounter{tocdepth}{2}
\tableofcontents
\newpage
\pagenumbering{arabic}


%--------------------Reference Documents ---------------------------------------
\section{Reference Documents}
\begin{enumerate}
\item PUSS154212 - System Requirements Specification for the current project \label{refdocs:srs}
\item Programvaruutveckling för Stora System - Projekthandledning v2.2 (\textit{Institutionen för datavetenskap}, Lunds Univeritet 2015) \label{refdocs:projekthandledning}
\item PUSS154213 - Software Verification and Validation Specification \label{redocs:SVVS}
\item PUSS154253 - Test Matrices for SVVS. \label{refdocs:matrices}
\end{enumerate}

%--------------------Introduction ---------------------------------------
\section{Introduction}
For simplicity the test instructions are in appenidices, \ref{appendix:section:functiontest} and \ref{appendix:section:systemtest}.

Have an ice day!

%--------------------Appendix A: Function test Specification ----------------
\newpage
\begin{appendices}

\section{Function Test Instructions} \label{appendix:section:functiontest}
This is appendix A where we list all function test instructions.

\subsection{MyDevices View Test Instructions}
\begin{testlist}

    \item 
    	\begin{precondition}
    		\item Telephone is on
    		\item Application installed but not running.
    	\end{precondition}
    	\begin{instruction}
    		\item Locate the application icon on the telephone.
    		\item With your right index finger press the application icon.
	    	\item Wait.
    		\item Look at the screen and confirm the resemblance with figure \textbf{blurp} in \ref{refdocs:srs}.
    	\end{instruction}
    	\begin{postcondition}
    		\item The application is running and the MyDevices screen is shown.
    	\end{postcondition}
    %Test description: The first screen that is shown on startup is the MyDevicesView (Req. 5.2.1).
    
	\item The list of available devices is empty on application start up. (Req. 5.2.2)
   
    \item The list on the MyDevices view is scrollable. (Req. 5.2.3)
   
    \item The devices on the list are selectable. (Req 5.2.4)
   
    \item Only one device can be selected at a time. (Req. 5.2.5)
   
    \item When no device is selected and the "Control Device" -button is pressed, a pop-up message "Please select a device" is displayed. (Req. 5.2.6)
   
    \item Sensors are displayed in the list of available devices with "Sensor" as name, and it's MAC address as address and their indentifier as id. (Req. 5.2.7)
   
    \item Light bulbs are displayed in the list of available devices with "Light Bulb" as name and it's MAC address as address and their indentifier as id. (Req. 5.2.8)
   
    \item The "Get Devices" -button performs a scan for available devices when pressed. (Req. 5.2.9)
   
    \item When the back button is pressed the application is closed (Req. 5.2.10)
    
    % Nytt requirement!
    \item The layout of the MyDevices View resemble figure 1 in appendix  Ref \ref{refdocs:srs} (5.2.11).
\end{testlist}

%--------------------------Sensor view tests --------------------------------------
\subsection{Sensor View Test Instructions}
\begin{testlist}
\item When the "Control Device"-button in the MyDevices View is pressed and a sensor is selected, the Sensor view is opened (Req. 5.3.1).

\item The sensor name and mac-address is shown in the top of the view (Req. 5.3.2, 5.3.3).
 
\item It is possible to change the on/off -status of the selected sensor with a switch (Req. 5.3.4).

\item There are text fields preceded by "T", "P", "H", "M", "G", "A" that are used to, respectively, display temperature, pressure, humidity, magnetic field strength, gyroscopic data and acceleration (Req. 5.3.5, 5.3.6, 5.3.7, 5.3.8, 5.3.9, 5.3.10).

\item By pressing the corresponding "Get"-button, the values of the temperature, pressure, humidity, magnetic field strength, qyroscopic and acceleration sensors are retrieved if available and displayed (Req. 5.3.11, 5.3.12, 5.3.13, 5.3.14, 5.3.15, 5.3.16).

\item The "Get All" -button gets the values for all six sensors and displays them (Req. 5.3.17).

\item The "Clear All" button clears all sensor text fields from data (Req. 5.3.18).

\item If there is no data to retrieve for any of the physical quantities: temperature, pressure, humidity, magnetic field strength, gyroscopic data and acceleration when the corresponding "Get" button is pressed the corresponding, text fields display "No data available" (Req. 5.3.19, 5.3.20, 5.3.21, 5.3.22, 5.3.23, 5.3.24).

\item The on/off-switch is set according to the information from the REST API (Req. 5.3.25).

\item When the back button is pressed in the Sensor View, the MyDevices View is opened (Req. 5.3.26).

\item When the sensor view is opened the temperature, pressure, humidity, magnetic field strength, gyroscopic data and acceleration text fields are empty (Req. 5.3.27).

% Nytt requirement!
\item The layout of the Sensor View resemble figure 2 in appendix  Ref \ref{refdocs:srs} (Req. 5.3.28).

\end{testlist}

\subsection{Light Bulb View Test Instructions}
\begin{testlist}
	\item The Light Bulb View opens when a light bulb is chosen in the MyDevices View and the "Control device" button is pressed. (Req 5.4.1)
	
	\item The name of the selected light bulb is shown at the top of the View (Req 5.4.2).
  
    \item The selected light bulb can be turned on/off with a switch (Req. 5.4.3). 
    
    \item The field of R-, G-, B-, W-value is editable and preceded by "R:", "G:", "B:" and "W:" respectively (Req. 5.4.4, 5.4.5, 5.4.6, 5.4.7). 
    
	\item When the Light Bulb View is opened, the fields are empty (Req. 5.4.8).

	\item The "Get"-button retrieves the R-, G-, B-, W-values and present them in their corresponding fields (Req. 5.4.9). 

	\item The "Set button" sets the color of the light bulb (Req. 5.4.10).

	\item If an input value is left blank the value is interpreted as 00 (Req. 5.4.11) .   
    
    \item The fields only accepts two characters that represent hexadecimal numbers (e.g. 00 to FF and all combinations inbetween) (Req 5.4.12, Req 5.4.13).
    
    \item A pop-up message saying "Color successfully changed" is displayed when the values of the light bulb were successfully set. (Req 5.4.14)
    
    \item A pop-up message saying "Error: Could not change color." is displayed when the values of the light bulb were unsuccessfully set. (Req 5.4.15)
       
    \item When the light bulb is off, the "Set"-button is unavailable (Req. 5.4.16).
    
    \item When the back button is pressed the system switches to MyDevices View (Req. 5.4.17).
    
    % Nytt requirement!
    \item The layout of the Light Bulb View resemble figure 3 in appendix  Ref \ref{refdocs:srs} (Req. 5.4.18).

\end{testlist}	

%--------------------Appendix B: System Test Specification ----------------
\newpage

\section{System Test Instruction} \label{appendix:section:systemtest}
This is appendix B where we list all system test specifications.

\subsection{Use Cases}
\begin{testlist}
	\item 
		\begin{precondition}
			\item The application is running and MyDevices view is displayed.
			\item There is a lightbulb and a sensor device within scan range of the MVD.
			\item No other devices are within range of the MVD.
		\end{precondition}
		\begin{instruction}
			\item With your right index finger press the \emph{Get Devices} button.
			\item Verify that the Light bulb is shown.
			\item Verify that the Sensor device is shown.
		\end{instruction}
		\begin{postcondition}
			\item The light bulb is displayed in the MyDevices view.
		 	\item The sensor device is displayed in the MyDevices view.
		\end{postcondition}
	%SVVS: Scenario 5.1.1 in Ref \ref{refdocs:srs} is supported (Req. 5.1.1).

	\item 
	\begin{precondition}
		\item The application is running and MyDevices view is displayed.
		\item No devices are within range of the MVD.
	\end{precondition}
	\begin{instruction}
			\item With your right index finger press the \emph{Get Devices} button.
			\item Verify that a pop-up message with the text \emph{No devices found} is shown.
	\end{instruction}
	\begin{postcondition}
		\item No devices are connected.
	\end{postcondition}
	%SVVS: Exception 1 described in scenario 5.1.1 can be generated by removing the devices from range while attempting scenario 5.1.1 (Req 5.1.1).
	
	\item Scenario 5.1.2 in Ref \ref{refdocs:srs} is supported (Req. 5.1.2).
	
	\item Exception 1 in scenario 5.1.2 can be generated by not selecting a device in step 1 (Req. 5.1.2).
	
	\item Scenario 5.1.3 in Ref \ref{refdocs:srs} is supported (Req. 5.1.3).
	
	\item Exception 1 described in scenario 5.1.3 can be generated by not selecting a device in step 1 (Req. 5.1.3). 
	
	\item Scenario 5.1.4 in Ref \ref{refdocs:srs} is supported (Req. 5.1.4).
	
	\item Scenario 5.1.5 in Ref \ref{refdocs:srs} is supported (Req. 5.1.5).
	
	\item Scenario 5.1.6 in Ref \ref{refdocs:srs} is supported (Req. 5.1.6).
	
	\item Scenario 5.1.7 in Ref \ref{refdocs:srs} is supported (Req. 5.1.7).
	
	\item Scenario 5.1.8 in ref \ref{refdocs:srs} is supported (Req. 5.1.8).

	\item Scenario 5.1.9 in Ref \ref{refdocs:srs} is supported (Req. 5.1.9).
	
	\item If some data is unavailable when attempting scenario 5.1.9, the text in the corresponding field is set to "No data available." (Req. 5.1.9).
	
	\item Scenario 5.1.10 in Ref \ref{refdocs:srs} is supported (Req. 5.1.10).
	
	\item If some data is unavailable when attempting scenario 5.1.10, the text in the corresponding field is set to "No data available." (Req. 5.1.10).
	
	\item Scenario 5.1.11 in Ref \ref{refdocs:srs} is supported (Req. 5.1.11).
	
	\item If some data is unavailable when attempting scenario 5.1.11, the text in the corresponding field is set to "No data available." (Req. 5.1.11).
	
	\item Scenario 5.1.12 in Ref \ref{refdocs:srs} is supported (Req. 5.1.12).
\end{testlist}

\subsection{Quality Test Instructions}

\begin{testlist}
	\item Test of usability using persons without prior knowledge of the project or the app (Req. 6.1).
	
	\item The response time for any interaction with the system is below two seconds (Req. 6.2).
	
	\item The time-out time for the system is 15 seconds (Req. 6.3). 
	
\end{testlist}

\clearpage

\end{appendices}


\end{document}