\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{float}

\title{SRS - Software Requirements Specification}

\date{\today}

\begin{document}

\maketitle


\pagebreak
\setcounter{tocdepth}{2}
\tableofcontents
\pagebreak

\section{Introduction}
This document describes the requirements created for the Application to control MVD devices. The application controls both the sensor device and a light bulb.
\section{Reference documents}
Reference document: PUS15001.
\section{Background and goals}
\subsection{Main goals}
The application contains three views named MyDevices view, Sensor Device view and Light Bulb view. The user should through the application be able to control MVD devices.
\subsection{Actors and their objectives}
\textbf{Lamp Controller Android Application} is used as a controller for the light bulbs. Can be used to scan for devices, talk to a specific sensor or talk to a light bulb.
\newline \newline
\textbf{Back End} is the endpoint which the app talks to, to control the light bulbs and to get sensor data. Is accessed through a REST API. 
\section{Terminology}
\textbf{REST API}, representational state transfer application  program interface. An HTTP endpoint to which the application talks in HTTP packages in order to communicate with the back end. 
\newline \newline
\textbf{MVD} Minimal viable device to scan for Bluetooth Low Energy (BLE) devices, collect and pass the data to the remote server using MQTT protocol.
\section{Functional requirements}
\section{Quality requirements}
\section{Project requirements}
              
\end{document}